Thread Management for High Performance Database Systems - Design and Implementation \\{\large Technical Report

### 2018-07-27 Presentations/Paper/paper_thread_pool.tex
Preparation for technical report

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{multicol}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{listings}

@@

\title{Thread Pool in GeckoDB/BOLSTER - Implementing a Thread Pool for a High Performance Database System \\}

\author{
	\IEEEauthorblockN{Robert Jendersie, Johannes Wuensche, Johann Wagner, Marten Wallewein-Eising}
	\IEEEauthorblockA{\textit{Otto-von-Guericke University} \\
		Magdeburg, Germany \\
		\emph{firstname}.\emph{lastname}@st.ovgu.de} \and
}

@@

To overcome these drawbacks, we integrate an optimised thread pool in BOLSTER. Along with the implementation, we measure the performance of the primitives to determine the thread pool overhead. Additionally, we measure metrics like \emph{waiting and busy time} of threads to evaluate correct thread pool sizes for the considered use cases. In this work we make the following contributions:
\begin{itemize}
	\item We describe our design and implementation of the thread pool
	\item We evaluate the possibility to wait for a group of task in the calling thread
	\item We compare our thread pool against the existing implementation in BOLSTER
	\item We measure and evaluate additional statistics for different thread pool configurations
\end{itemize}
We organized the rest of the paper as follows. In Section 2, we give preliminaries about the considered task configuration and about thread safe access of memory. In Section 3, we show our design and implementation of the thread pool and examine our experimental environment in Section 4. In Section 5, we describe the results of our performance evaluation. In Section 6, we name related work and state our conclusion and future work in Section 7.

@@

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{multicol}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{url}

@@

\title{Thread Management for High Performance Database Systems - Design and Implementation \\{\large Technical Report}\\}

\author{
	\IEEEauthorblockN{Robert Jendersie, Johannes Wuensche, Johann Wagner, \\Marten Wallewein-Eising, Marcus Pinnecke, Gunter Saake}
	\IEEEauthorblockA{\textit{Database and Software Engineering Group, Otto-von-Guericke University} \\
		Magdeburg, Germany \\
		\emph{firstname}.\emph{lastname}@ovgu.de} \and
}

@@

To overcome these drawbacks, we integrate an optimised thread pool in BOLSTER. Along with the implementation, we measure the performance of the primitives to determine the thread pool overhead. Additionally, we measure metrics like \emph{waiting and busy time} of threads to evaluate correct thread pool sizes for the considered use cases.

In this work we make the following contributions:
\begin{itemize}
	\item \textbf{Design and Implementation} We describe our design and implementation of the thread pool
	\item \textbf{Waiting Strategies} We evaluate the possibility to wait for a group of task in the calling thread
	\item \textbf{Evaluation} We compare our thread pool against the existing implementation in BOLSTER
	\item \textbf{Statistics per Configuration} We measure and evaluate additional statistics for different thread pool configurations
\end{itemize}
We organized the rest of the paper as follows. In Section 2, we give preliminaries about the considered task configuration and about thread safe access of memory. In Section 3, we show our design and implementation of the thread pool and examine our experimental environment in Section 4. In Section 5, we describe the results of our performance evaluation. In Section 6, we name related work and state our conclusion and future work in Section 7.

@@

\section{Acknowledgements}
This work was partially funded by the DFG (grant no.: SA 465/50-1).
